Matched Source Waveform Inversion for Transmitted Waves

### 2024-05-29 repro/papers/awinum/paper.tex
examples with more extreme oblate lens

The FWI iteration starting at the MSWI result has effectively achieved
the global minimum of the FWI objective function: the data match is
very close. The combination of MSWI followed by FWI has fit the data
starting from the homogeneous initial model, a result that cannot be
reached by FWI alone.

@@

Our next two examples use another lens model, somewhat deeper (with a
minimum bulk modulus of 2 GPa in the center), therefore more
refractive, and extended in the
horizontal direction. See Figure \ref{fig:cwm}. As is the case with
the circular lens, this oblate lens is smooth to adequate numerical
approximation.

\plot{cwm}{width=\textwidth}{Oblate lens model.}

The first example using this model has exactly the same acquisition
geometry as was used in the circular lens example: 20 sources at x =
3000 m, 201 receivers at x = 5000 m, spaced as described in the
previous section. The data is shown in Figure \ref{fig:cowd20}.

\plot{cowd20}{width=\textwidth}{Data using model shown in Figure
  \ref{fig:cwm}, same source-receiver geometry as for circular lens
  data (Figure \ref{fig:cwd20}).}

The stronger refraction produced by this model produces a near-focus in
the center of the source-receiver line. In fact, the ray field is
triplicated, but the smearing effect of finite bandwidth obscures this
detail, and the data can be (just!) regarded as exhibiting a single
arrival on an identifiable wavefront.

@@

Application of steepest descent to the MSWI objective (with the same
parameters as in the previoius example) results in the model depicted
in Figure \ref{fig:nqcaustic20mestmswi}, and reduces the objective by
almost a factor of 7 (from 2.76 $\times 10^{-2}$ to 4.1 $\times
10^{-3}$ and the gradient norm by two full orders of magnitude. Data
simulated with this model is shown in Figure
\ref{fig:nqcaustic20resimmestmswi}, and the residual in Figure
\ref{fig:nqcaustic20residmestmswi}.

\plot{nqcaustic20mestmswi}{width=\textwidth}{Result of 8 MSWI
  iterations applied to the data in Figure \ref{fig:cowd20}, beginning
  at the homogeneous model.}

\multiplot{2}{nqcaustic20resimmestmswi,nqcaustic20residmestmswi}{width=0.45\textwidth}{a: Data
  corresponding to MSWI result shown in Figure
  \ref{fig:nqcaustic20mestmswi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:nqcaustic20resimmestmswi} and target data
  \ref{fig:cowd20}.}

The change in adaptive filters between the homogenous initial model
and the MSWI inversion is shown in Figures
\ref{fig:nqcaustic20uest0} and \ref{fig:nqcaustic20uestmswi}. The
reduction in energy dispersion is evident.

\multiplot{2}{nqcaustic20uest0,nqcaustic20uestmswi}{width=0.45\textwidth}{a:
  adaptive filter estimate for homogeneous initial model, data of
  Figure \ref{fig:cowd20}; b: adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:nqcaustic20mestmswi}.}

These results render the MSWI inversion result a plausible initial
estimate for FWI. Twelve FWI iterations applied to the data in Figure \ref{fig:cowd20}, starting at the model of
Figure \ref{fig:nqcaustic20mestmswi}, result in the
model shown in Figure \ref{fig:nqcaustic20mestmswifwi}, at which the
FWI objective has decreased from $\approx 5.5$ to $\approx 0.13$, that
is, by more than 97\%. The gradient decreases by approximately the
same factor. This is evident in the plots of simulated data and
residual (Figures \ref{fig:nqcaustic20resimmestmswifwi} and
\ref{fig:nqcaustic20residmestmswifwi}). Finally, energy dispresion
from $t=0$ has nearly disappeared from the adaptive filter computed
from this FWI +MSWI result (Figure \ref{fig:nqcaustic20uest1}).

\plot{nqcaustic20mestmswifwi}{width=\textwidth}{a: Bulk modulus produced by 12
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:cowd20}, and starting at the MSWI
  result shown in Figure \ref{fig:nqcaustic20mestmswi}.}

\multiplot{2}{nqcaustic20resimmestmswifwi,nqcaustic20residmestmswifwi}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:nqcaustic20mestmswifwi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:nqcaustic20resimmestmswifwi} and target data
  \ref{fig:cowd20}.}

\plot{nqcaustic20uest1}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:nqcaustic20resimmestmswi}) to oblate lens
  data (Figure \ref{fig:cowd20}). Dispersion away from 
  away from $t=0$ has almost disappeared, showing that the resimulated
  data is nearly a perfect kinematic match with the target data.}

The second example based on the target model in Figure \ref{fig:cwm}
differs from the first {\em only} in that the sources and receivers
have been moved further away from each other: the sources lie on the
line $x=2000$, the receivers on $x=6000$. That is, the source-receiver
offset has been doubled. Otherwise, all aspects of data generation are
the same, and produce the data shown in Figure \ref{fig:fcwd20}.

\plot{fcwd20}{width=\textwidth}{Data generated using the same inputs
  as in Figure \ref{fig:cowd20}, but with sources moved to $x=2000$
  and receivers to $x=6000$.}

@@

As before, we compute the adaptive filter required to produce the data
of Figure \ref{fig:fcwd20} from the corresponding homogeneous medium data (Figure
\ref{fig:chwd20}). This filter, displayed in \ref{fig:caustic20uest0},
shows that for most traces, two or more energy peaks appear in the
adaptive filter, forced by the need to match multiple energy peaks in
the target data with the single energy peak in the homogeneous medium
data.

Using the same parameters (tolerance of 0.01 for the normal residual
in the CG iteration, 12 steps of steepest descent) produces the model
estimate depicted in Figure \ref{fig:caustic20mestmswi}. The overall
shape suggests decrease in bulk modulus in more or less the right
place, but the minimum bulk modulus attained (3.15 GPa) is considerably larger
than the target's, suggesting that the amount of refraction is
considerably less. That guess is verified by resimulating the data
(Figure \ref{fig:caustic20resimmestmswi}): the predicted data does not
exhibit triplication. The computed adaptive filter (Figure 
\ref{fig:caustic20uestmswi}) appears to attempt a compromise between
earlier and later arrivals. Most importantly, the final gradient norm
is approximately 5\% of the initial, suggesting that the minimizer has
not been approximated as well as was the case in the previous
examples. FWI initiated at the MSWI estimate gives an evidently
cycle-skipped model estimate (Figure \ref{fig:caustic20mestmswifwi}),
with unsatisfactory resimulation and residual (Figures
\ref{fig:caustic20resimmestmswifwi},
\ref{fig:caustic20residmestmswifwi}), and considerable energy spread
ion the estimated adaptive filter (Figure \ref{fig:caustic20uest1}.

\plot{caustic20uest0}{width=\textwidth}{Adaptive filter required to produce the data
of Figure \ref{fig:fcwd20} from corresponding homogeneous medium data (Figure
\ref{fig:chwd20}).}

\plot{caustic20mestmswi}{width=\textwidth}{Result of 12 MSWI
  iterations applied to the data in Figure \ref{fig:fcwd20}, beginning
  at the homogeneous model.}

\multiplot{2}{caustic20resimmestmswi,caustic20residmestmswi}{width=0.45\textwidth}{a: Data
  corresponding to MSWI result shown in Figure
  \ref{fig:caustic20mestmswi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:caustic20resimmestmswi} and target data
  \ref{fig:fcwd20}.}

\plot{caustic20uestmswi}{width=\textwidth}{Adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:caustic20mestmswi}.}

\plot{caustic20mestmswifwi}{width=\textwidth}{Bulk modulus produced by 12
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:fcwd20}, and starting at the MSWI
  result shown in Figure \ref{fig:caustic20mestmswi}.}

\multiplot{2}{caustic20resimmestmswifwi,caustic20residmestmswifwi}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:caustic20mestmswifwi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:caustic20resimmestmswifwi} and target data
  \ref{fig:fcwd20}.}

\plot{caustic20uest1}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:caustic20resimmestmswi}) to oblate lens
  data (Figure \ref{fig:fcwd20}). Considerable energy dispersion away
  from $t=0$ remains, showing that the inverted model does not match
  data kinematics well.}

As noted above, the reduction in gradient norm achieved in 12 steepest
descent iterations for this example is not as great as was the case in
the two previous exmaples: this appears to be a more difficult
optimization. Accordingly, we perform 12 additional iterations of
steepest descent. The final gradient norm is $\approx 1.1 \times
10^{-11}$, an order of magnitude less than the final norm achieved in
the first 12 iterations and well over two orders of magnitude less
than the initial gradient norm of $\approx 5.24 \times 10^{-9}$. The
depression in the center of the estimated bulk modulus has deepened
(Figure \ref{fig:caustic20mestmswicont}) (2.53 GPa, vs 3.15 GPa at the
end of the first 12 iterations). While it is stiil insufficiently
refractive to produce triplication, the resulting resimulation has
increased in magnitude for the central tracess, indicating approach to a focus, and delayed by
roughly a half-wavelength compared to the corresponding result at the
end of the first MSWI iteration. As the remaining figures show, FWI
starting from this result is much more satisfactory. The latest
arrival for the central traces still does not have quite correct
amplitude, but all data phases are correct.

\plot{caustic20mestmswicont}{width=\textwidth}{Result of 24 MSWI
  iterations applied to the data in Figure \ref{fig:fcwd20}, beginning
  at the homogeneous model.}

\multiplot{2}{caustic20resimmestmswicont,caustic20residmestmswicont}{width=0.45\textwidth}{a: Data
  corresponding to MSWI result shown in Figure
  \ref{fig:caustic20mestmswicont}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:caustic20resimmestmswicont} and target data
  \ref{fig:fcwd20}.}

\plot{caustic20uestmswicont}{width=\textwidth}{Adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:caustic20mestmswicont}.}

\plot{caustic20mestmswifwicont}{width=\textwidth}{Bulk modulus produced by 25
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:fcwd20}, and starting at the MSWI
  result shown in Figure \ref{fig:caustic20mestmswicont}.}

\multiplot{2}{caustic20resimmestmswifwicont,caustic20residmestmswifwicont}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:caustic20mestmswifwicont}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:caustic20resimmestmswifwicont} and target data
  \ref{fig:fcwd20}.}

\plot{caustic20uest2}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:caustic20resimmestmswicont}) to oblate lens
  data (Figure \ref{fig:fcwd20}). Dispersion away from 
  away from $t=0$ has almost disappeared, showing that the resimulated
  data is nearly a perfect kinematic match with the target data.}

>>>>

The FWI iteration starting at the MSWI result has effectively achieved
the global minimum of the FWI objective function: the data match is
very close. The combination of MSWI followed by FWI has fit the data
starting from the homogeneous initial model, a result that was not obtained
by FWI alone with the algorithmic choices made here.

@@

Our next two examples use another lens model, somewhat deeper (with a
minimum bulk modulus of 2 GPa in the center), therefore more
refractive, and extended in the
horizontal direction. See Figure \ref{fig:dcwm}. As is the case with
the circular lens, this oblate lens is smooth to adequate numerical
approximation.

\plot{dcwm}{width=\textwidth}{Oblate lens model.}

The first example using this model has exactly the same acquisition
geometry as was used in the circular lens example: 20 sources at x =
3000 m, 201 receivers at x = 5000 m, spaced as described in the
previous section. The data is shown in Figure \ref{fig:dcowd20}.

\plot{dcowd20}{width=\textwidth}{Data using model shown in Figure
  \ref{fig:dcwm}, same source-receiver geometry as for circular lens
  data (Figure \ref{fig:cwd20}).}

The stronger refraction produced by this model produces a visible triplication
the center of the source-receiver line, and in fact in all parts of
the data, although the smearing effect of finite bandwidth obscures this
detail in many placed. So most of the data can be (just!) regarded as exhibiting a single
arrival on an identifiable wavefront.

@@

Application of steepest descent to the MSWI objective (with the same
parameters as in the previoius example) results in the model depicted
in Figure \ref{fig:mnqcaustic20mestmswi}, and reduces the objective to
roughly 20\% of its initial value, and the gradient norm to 7.5\%. Data
simulated with this model is shown in Figure
\ref{fig:mnqcaustic20resimmestmswi}, and the residual in Figure
\ref{fig:mnqcaustic20residmestmswi}.

\plot{mnqcaustic20mestmswi}{width=\textwidth}{Result of 8 MSWI
  iterations applied to the data in Figure \ref{fig:dcowd20}, beginning
  at the homogeneous model.}

\multiplot{2}{mnqcaustic20resimmestmswi,mnqcaustic20residmestmswi}{width=0.45\textwidth}{a: Data
  corresponding to MSWI result shown in Figure
  \ref{fig:mnqcaustic20mestmswi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:mnqcaustic20resimmestmswi} and target data
  \ref{fig:dcowd20}.}

The change in adaptive filters between the homogenous initial model
and the MSWI inversion is shown in Figures
\ref{fig:mnqcaustic20uest0} and \ref{fig:mnqcaustic20uestmswi}. The
reduction in energy dispersion is evident.

\multiplot{2}{mnqcaustic20uest0,mnqcaustic20uestmswi}{width=0.45\textwidth}{a:
  adaptive filter estimate for homogeneous initial model, data of
  Figure \ref{fig:dcowd20}; b: adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:mnqcaustic20mestmswi}.}

These results render the MSWI inversion result a plausible initial
estimate for FWI. Twelve FWI iterations applied to the data in Figure \ref{fig:dcowd20}, starting at the model of
Figure \ref{fig:mnqcaustic20mestmswi}, result in the
model shown in Figure \ref{fig:mnqcaustic20mestmswifwi}, at which the
FWI objective has decreased to 4\% of its initial value. That is, the
RMS error between data and predicted data has been reduced to
approximately 20\% of its initial value; the gradient
decreases by a slightly larger factor. The reduction obtained is evident in the plots of simulated data and
residual (Figures \ref{fig:mnqcaustic20resimmestmswifwi} and
\ref{fig:mnqcaustic20residmestmswifwi}). Residual energy is
concentrated in later arrivals in the
central zone, suggesting that the model shown in Figure
\ref{fig:mnqcaustic20mestmswifwi} may lie in the basin of global minimization. Finally, energy dispresion
from $t=0$ has nearly disappeared from the adaptive filter computed
from this FWI +MSWI result, again except for some traces in the
central zone (Figure \ref{fig:mnqcaustic20uest1}).

\plot{mnqcaustic20mestmswifwi}{width=\textwidth}{a: Bulk modulus produced by 12
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:dcowd20}, and starting at the MSWI
  result shown in Figure \ref{fig:mnqcaustic20mestmswi}.}

\multiplot{2}{mnqcaustic20resimmestmswifwi,mnqcaustic20residmestmswifwi}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:mnqcaustic20mestmswifwi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:mnqcaustic20resimmestmswifwi} and target data
  \ref{fig:dcowd20}.}

\plot{mnqcaustic20uest1}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:mnqcaustic20resimmestmswi}) to oblate lens
  data (Figure \ref{fig:dcowd20}). Dispersion away from 
  away from $t=0$ has almost disappeared, showing that the resimulated
  data is nearly a perfect kinematic match with the target data.}

The second example based on the target model in Figure \ref{fig:dcwm}
differs from the first {\em only} in that the sources and receivers
have been moved further away from each other: the sources lie on the
line $x=2000$, the receivers on $x=6000$. That is, the source-receiver
offset has been doubled. Otherwise, all aspects of data generation are
the same, and produce the data shown in Figure \ref{fig:dcwd20}.

\plot{dcwd20}{width=\textwidth}{Data generated using the same inputs
  as in Figure \ref{fig:dcowd20}, but with sources moved to $x=2000$
  and receivers to $x=6000$.}

@@

As before, we compute the adaptive filter required to produce the data
of Figure \ref{fig:dcwd20} from the corresponding homogeneous medium data (Figure
\ref{fig:chwd20}). This filter, displayed in \ref{fig:mcaustic20uest0},
shows that for most traces, two or more major energy peaks appear in the
adaptive filter, forced by the need to match multiple energy peaks in
the target data with the single energy peak in the homogeneous medium
data.

Using the same parameters (tolerance of 0.01 for the normal residual
in the CG iteration, same smoothing operator as inverse weight
defining norm in model space) 12 steps of steepest descent applied to
the MSWI objective produces the model
estimate depicted in Figure \ref{fig:mcaustic20mestmswi}. The overall
decrease in bulk modulus is correct, but the minimum bulk modulus attained (2.8 GPa) is considerably larger
than the target's, and moreover is concentrated around the source
line, suggesting that the amount of refraction produced by this model is
considerably less. That guess is verified by resimulating the data
(Figure \ref{fig:mcaustic20resimmestmswi}): the predicted data does not
exhibit triplication. The computed adaptive filter (Figure 
\ref{fig:mcaustic20uestmswi}) appears to attempt a compromise between
earlier and later arrivals. Most importantly, the final gradient norm
is approximately 18\% of the initial, suggesting that the minimizer has
not been approximated as well as was the case in the previous
examples. FWI initiated at the MSWI estimate gives an evidently
cycle-skipped model estimate (Figure \ref{fig:mcaustic20mestmswifwi}),
with unsatisfactory resimulation and residual (Figures
\ref{fig:mcaustic20resimmestmswifwi},
\ref{fig:mcaustic20residmestmswifwi}), and considerable energy spread
ion the estimated adaptive filter (Figure \ref{fig:mcaustic20uest1}.

\plot{mcaustic20uest0}{width=\textwidth}{Adaptive filter required to produce the data
of Figure \ref{fig:dcwd20} from corresponding homogeneous medium data (Figure
\ref{fig:chwd20}).}

\plot{mcaustic20mestmswi}{width=\textwidth}{Result of 12 MSWI
  iterations applied to the data in Figure \ref{fig:dcwd20}, beginning
  at the homogeneous model.}

\multiplot{2}{mcaustic20resimmestmswi,mcaustic20residmestmswi}{width=0.45\textwidth}{a: Data
  corresponding to MSWI result shown in Figure
  \ref{fig:mcaustic20mestmswi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:mcaustic20resimmestmswi} and target data
  \ref{fig:dcwd20}.}

\plot{mcaustic20uestmswi}{width=\textwidth}{Adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:mcaustic20mestmswi}.}

\plot{mcaustic20mestmswifwi}{width=\textwidth}{Bulk modulus produced by 12
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:dcwd20}, and starting at the MSWI
  result shown in Figure \ref{fig:mcaustic20mestmswi}.}

\multiplot{2}{mcaustic20resimmestmswifwi,mcaustic20residmestmswifwi}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:mcaustic20mestmswifwi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:mcaustic20resimmestmswifwi} and target data
  \ref{fig:dcwd20}.}

\plot{mcaustic20uest1}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:mcaustic20resimmestmswi}) to oblate lens
  data (Figure \ref{fig:dcwd20}). Considerable energy dispersion away
  from $t=0$ remains, showing that the inverted model does not match
  data kinematics well.}

As noted above, the reduction in MSWI gradient norm achieved in 12 steepest
descent iterations for this example is not as great as was the case in
the two previous exmaples: this appears to be a more difficult
optimization. Accordingly, we perform 12 additional iterations of
steepest descent applied to the MSWI objective, starting withe the
result (Figure \ref{fig:mcaustic20mestmswi}) of the first 12
iterations. The objective decreases by roughly 0.8, the gradient by
0.5. Inspection of the model so obtained (Figure
\ref{fig:mcaustic20mestmswicont}) shows that the minimum bulk modulus
has decreased (2.09 GPa, vs 2.8  GPa at the
end of the first 12 iterations), however the smallest values are even
more concentrated around the source locations, and the resimulated
data with this model is if anything less similar to the data than was
the case at the end of the first 12 iterations (Figures
\ref{fig:mcaustic20resimmestmswicont},
\ref{fig:mcaustic20residmestmswicont}). The adaptive filter is no more
focused at $t=0$ than was the case at the end of the first 12
iterations: it appears to have adjusted the compromise between shifts
to fit early and late arrivals, nothing more (Figure \ref{fig:mcaustic20uestmswicont}).

\plot{mcaustic20mestmswicont}{width=\textwidth}{Result of 24 MSWI
  iterations applied to the data in Figure \ref{fig:dcwd20}, beginning
  at the homogeneous model.}

\multiplot{2}{mcaustic20resimmestmswicont,mcaustic20residmestmswicont}{width=0.45\textwidth}{a: Data
  corresponding to MSWI result shown in Figure
  \ref{fig:mcaustic20mestmswicont}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:mcaustic20resimmestmswicont} and target data
  \ref{fig:dcwd20}.}

\plot{mcaustic20uestmswicont}{width=\textwidth}{Adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:mcaustic20mestmswicont}.}

This result (Figure \ref{fig:mcaustic20mestmswicont}) is actually a
{\em worse} initial estimate for FWI than was the model obtained after
12 steepet descent iterations. We
performed 25 steps of steepest descent applied to the FWI objective
with the model in Figure \ref{fig:mcaustic20mestmswicont} as initial
estimate, resulting in the obviously cycle-skipped model displayed in
Figure \ref{fig:mcaustic20mestmswifwicont}. The residual (Figure
\ref{fig:mcaustic20residmestmswifwicont} and adaptive filter (Figure
\ref{fig:mcaustic20uest2}) have actually deteriorated relative to
those obtained before.

\plot{mcaustic20mestmswifwicont}{width=\textwidth}{Bulk modulus produced by 25
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:dcwd20}, and starting at the MSWI
  result shown in Figure \ref{fig:mcaustic20mestmswicont}.}

\multiplot{2}{mcaustic20resimmestmswifwicont,mcaustic20residmestmswifwicont}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:mcaustic20mestmswifwicont}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:mcaustic20resimmestmswifwicont} and target data
  \ref{fig:dcwd20}.}

\plot{mcaustic20uest2}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:mcaustic20resimmestmswicont}) to oblate lens
  data (Figure \ref{fig:dcwd20}). Dispersion away from 
  away from $t=0$ has almost disappeared, showing that the resimulated
  data is nearly a perfect kinematic match with the target data.}

The meaning of this result will be discussed further below. For now
merely note that the first example based on the oblate lens model in
Figure \ref{fig:dcwm} appeared to require more computational effort
than the cirular lens example to achieve a successful inversion,
whereas the second was an inversion failure even with considerably
more effort.
